Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-11-26 lloveras_2020.tex
algo de texto

\textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
OBS: Esta es la seleccion para las figuras 8 en adelante.}

@@

@@

@@

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2082} but for AWSoM results.}
\label{carmaps_awsom_2082}
\end{center}
\end{figure}

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2208} but for AWSoM results.}
\label{carmaps_awsom_2208}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel). In solid lines DEMT traced data and in dashed lines AWSoM data.}
\label{gradientes}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{Average fitted of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082(top panel) and CR-2208 (bottom panel). In solid lines DEMT traced results and in dashed lines AWSoM results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $\NCB\equiv N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082. In blue the data of DEMT are shown while those of AWSoM in red. In each panel the median $m$ is indicated.}

\label{histos_2082}
\end{center}
\end{figure}

@@

E) As the two rotations are strongly axis-symmetric we want to show the longitude-averaged results of DEMT at a low height, say 1.105 Rsun, along with AWSoM results. In the attached plot we show the DEMT and AWSoM longitude-averaged results at 1.105 Rsun in the top two panels (one for each rotation). The vertical lines indicate the longitude-averaged latitudes of the North and South OC boundary. The LOW panels show the longitude-averaged AWSoM wind speed Vr at 6 Rsun, where all field lines are open. The HCS location is indicated by the minimum of the speed curve. Everything to the South of the HCS maps down to the Southern OPEN region in the top panels, and the same for the Northern hemisphere. It is pretty obvious the ANTI-CORRELATION between the tomographic Ne at low heights (coronal source region of the wind) and the Vr.

This plot (E) has never been shown before and I believe it is a very nice result. There are of course previous studies on this, but this would be the first time this is evaluated with tomography. It is not the terminal speed, but it already shows the fast/slow components. We can show this, or we can go for more. Diego can QUANTIFY the correlation by carefully mapping all open field lines at 6 Rsun down to the DEMT region. He needs to code a bit more to achieve this goal, but we believe it is worth. With that tool done Diego can explore other terminal values of quantities of the AWSoM model and the DEMT results below (expansion factor maybe?). This will be nice to do also for the July-2-2019 Eclipse rotation that we will analyze after this paper.

>>>>

\textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
OBS: Esta es la seleccion para las figuras 8 en adelante. Citar numerical recipes seccion 15.2}

@@

\textcolor{red}{
*Comentarios descriptivos sobre las rotaciones:
-Simetria
-CH
-Matcheo entre open-closed boundaries y las estructuras termodinamicas.
}

@@

\textcolor{red}{
*Para las piernas trazadas que cumplen  |pearson de temp| > 0.5 se calcularon los gradientes de temp que cumplen test de hipotesis. Estos gradientes se muestran en la Figura \ref{gradientes} para las 3 regiones definidas para ambas rotaciones. Esto muestra up y down loops.
OBS: esto da pie a hablar y proponer mejoras en la conversion de modos de alfven. citar paper fede.
*Como el modelo awsom no presenta down loops, se selecciona de ahora en mas los loops con pearson de temp > 0.5
}
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel). In solid lines DEMT traced data and in dashed lines AWSoM data.}
\label{gradientes}
\end{center}
\end{figure}

\textcolor{red}{
For the two analyzed rotations, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all field lines that meet the criteria listed in Section \ref{trace} at $1.105\,\mrsun$.
}

@@

\textcolor{red}{Se presentan los resultados de Ne y Te del modelo AWSoM}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2082} but for AWSoM results.}
\label{carmaps_awsom_2082}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2208} but for AWSoM results.}
\label{carmaps_awsom_2208}
\end{center}
\end{figure}

\textcolor{red}{Se presentan los midpoints para awsom que lucen mas rellenos xq no hay down loops y todo es super suave.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{Average fitted of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel). In solid lines DEMT traced results and in dashed lines AWSoM results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

\textcolor{red}{
As way of example, Figure \ref{histos_2082} and \ref{histos_2208} shows the statistical results of both rotations for the three types of field lines traced with DEMT (blue) and AWSoM results (red). From left to right the panels show the statistical distribution of $\NCB$, $\lN$, $\aTm$ and $B_{\rm CB}$. }

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $\NCB\equiv N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082. In blue the data of DEMT are shown while those of AWSoM in red. In each panel the median $m$ is indicated.}
\label{histos_2082}
\end{center}
\end{figure}

@@

%E) As the two rotations are strongly axis-symmetric we want to show the longitude-averaged results of DEMT at a low height, say 1.105 Rsun, along with AWSoM results. In the attached plot we show the DEMT and AWSoM longitude-averaged results at 1.105 Rsun in the top two panels (one for each rotation). The vertical lines indicate the longitude-averaged latitudes of the North and South OC boundary. The LOW panels show the longitude-averaged AWSoM wind speed Vr at 6 Rsun, where all field lines are open. The HCS location is indicated by the minimum of the speed curve. Everything to the South of the HCS maps down to the Southern OPEN region in the top panels, and the same for the Northern hemisphere. It is pretty obvious the ANTI-CORRELATION between the tomographic Ne at low heights (coronal source region of the wind) and the Vr.

%This plot (E) has never been shown before and I believe it is a very nice result. There are of course previous studies on this, but this would be the first time this is evaluated with tomography. It is not the terminal speed, but it already shows the fast/slow components. We can show this, or we can go for more. Diego can QUANTIFY the correlation by carefully mapping all open field lines at 6 Rsun down to the DEMT region. He needs to code a bit more to achieve this goal, but we believe it is worth. With that tool done Diego can explore other terminal values of quantities of the AWSoM model and the DEMT results below (expansion factor maybe?). This will be nice to do also for the July-2-2019 Eclipse rotation that we will analyze after this paper.
